### 2021-01-18 BMC-Journal of Biomedical Semantics/submission 0/bmc_template/methodology.tex
Update methodology.tex

In order to process the EMR schema set $S$, we use the methodology shown in \textbf{algorithm}. For each data representation $s_i$, we first serialize its tables into Comma Separated Value (CSV) formatted flat files. Each table has a separate file, which contains the attribute names in the header and the data instances (following the same format and CSV struture), in subsequent lines. Each file is loaded in memory and converted into an algorithmic iterable structure. For each attribute, we then generate the suffix tree, which provides all possible substring representations contained within the attribute name. Then for each node of this suffix tree, if its length is greater than 2 (to avoid lookups for alphabets), we then query UMLS to retrieve its associated semantic concepts. \textbf{threshold}
If atleast one semantic concepts is found for the substring, we enhance the suffix tree, to now store the substring and its associated semantic concepts. We continue this process, untill all substrings have been processed. This is followed by syntactic type check of the attribute, which is based on its data. Here we determine, if the attribute values correspond to one of Integer, Float, Boolean, or String types. Additionally, we collect the values of each corresponding data cell, and determine the set of possible values in each case. 
This semantic enrichment from UMLS concepts and syntactic enrichment from attribute types, is then saved into persistent storage for further processing.

Meanwhile the process continues for the next attribute, then the next table, and finally the next system, till no further processing is possible. The flat enriched schema, following the design shown in \textbf{enrichedSchemaPic} provides the input to our knowledge base, whose creation is described in the next section.

>>>>

In order to process the EMR schema set $S$, we use the methodology shown in \textbf{algorithm}. For each data representation $s_i$, we first serialize its tables into Comma Separated Value (CSV) formatted flat files. Each table has a separate file, which contains the attribute names in the header and the data instances (following the same format and CSV struture), in subsequent lines. Each file is loaded in memory and converted into an algorithmic iterable structure. For each attribute, we then generate the suffix tree, which provides all possible substring representations contained within the attribute name. Then for each node of this suffix tree, if its length is greater than 2 (to avoid lookups for alphabets), we then query UMLS to retrieve its associated semantic concepts. \textbf{threshold}
If atleast one semantic concepts is found for the substring, we replace the substring with these concepts, and discard the substring otherwise, creating the Suffix Concept Tree (SCT). 
\textbf{Finally the equivalent embedding vector of each suffix's concept is placed in a structurally similar (to SCT)  tree embedding.
}
We continue this process, untill all substrings have been processed. This is followed by syntactic type check of the attribute, which is based on its data. Here we determine, if the attribute values correspond to one of Integer, Float, Boolean, or String types. Additionally, we collect the values of each corresponding data cell, and determine the set of possible values in each case. 
This semantic enrichment from UMLS concepts and syntactic enrichment from attribute types, is then saved into persistent storage for further processing.

Meanwhile the process continues for the next attribute, then the next table, and finally the next system, till no further processing is possible. The flat enriched schema, following the design shown in \textbf{enrichedSchemaPic} provides the input to our knowledge base. The logical structure of the enriched attribute, is represented in \textbf{figAttributeRepresentation}. Here, the elements of this particular data-structure are categorized into three parts. ``AttributeContext" contains the metadata conforming to an instance of the attribute's existence,  with its name, container table name and schema name, acting as a pointer, and schema version, source, and recorded date providing the version control features. In this manner, the attribute's fully qualified reference, along with its existential context is identified. ``AttributeType" then encapsulates the data type features of this attribute's instances, with its primitive data type, and values providing a representation of the attribute's instance. Finally, ``Attribute Semantics" holds, the semantic information of this attribute, in the form of its suffix tree, SCT and Tree Embedding.
A pair of this data-structure with distinct references, are then used as an input to the schema map generation process, which is explained in the next step.
